---
author: "Budapest Pizza Report - KFC (Kata, Fanni, Cosmin) Team"
date: 'October 25th, 2020'
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r , include = FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(readxl)
library(ggplot2)
library(moments)
data_in <- "C:/Users/acer/Desktop/OneDrive - Central European University/Courses/Fall_Term/Coding_1/data/Pizza"
pizza_data <- read_excel( paste0(data_in,"/raw/KFC-team_pizza_data.xlsx") )
```

The purpose of the report is to explore data about pizza prices in Budapest. The following repository contains the dataset, walkthrough explanation of the variables and the R codes used to create this descriptive analysis: [GitHub](https://github.com/cosmin-ticu/homework_codesANDmore_Coding1_MScBA/tree/master/Task1_KFC-team-coding)

### Data collection, difficulties & problems
The KFC team chose to limit the data collection to the Budapest area, with on-site prices being gathered only within the inner city districts (i.e. 2, 5, 6, 7, 8, 9, 11, 13), while delivery prices were documented irrespective of inner city district limits. The Google Maps API was used in order to compile the list (custom Google Maps shared lists) of on-site locations, gather customer reviews and compute the travel time between the restaurant and CEU. The choice of 0.5L sparkling water was convened with the drawback that the distribution of prices, brands and mark-up would be more heterogeneous than with the margherita pizza.

Variables like district, address and restaurant were added for reference purposes and to be able to have a unique identifier for every pizza place in case the dataset were to ever be expanded. The binary indicator variable 'delivery' which differentiates between restaurants' menu and online merchants' prices. The creation of this variable leads into the 'delivery_site' column which designates the online vendor. Lastly, since distance from the CEU Nador 15 building is hard to quantify with regards to driving a car (as there are numerous one-way streets and other detours which might add unnecessary distance units), the shortest walking distance was chosen and the metric of choice is minutes.

### Descriptive statistics for prices of margherita pizza and sparkling water
```{r, echo = FALSE, out.width='50%'}
pizza_stat <- pizza_data %>% summarise(
  n   = n(),
  Mean     = mean(price_pizza),
  Median   = median(price_pizza),
  Std      = sd(price_pizza),
  IQ_range = IQR(price_pizza), 
  Min      = min(price_pizza),
  Max      = max(price_pizza),
  Skew     = skewness(price_pizza))
beverage_stat <- pizza_data %>% summarise(
  n   = n(),
  Mean     = mean(price_swater),
  Median   = median(price_swater),
  Std      = sd(price_swater),
  IQ_range = IQR(price_swater), 
  Min      = min(price_swater),
  Max      = max(price_swater),
  Skew     = skewness(price_swater))
table_summary <- add_row(pizza_stat,beverage_stat)
knitr::kable(table_summary,caption="Summary statistics for pizza margherita prices (first row) and for sparkling water prices (second row) in Budapest")
```

The average price of pizza margherita is 1958.25 HUF. As for the sparkiling water, the average price is 518.5 HUF. The mean is higher than the median in case of the pizza and the water as well, indicating a somewhat skewed distribution with a long right tail. I the next section, the distribution will be illustrated by histograms.

### Histograms of product prices (kernel density showcases skewness)
The following plots describe the distribution of margherita pizza prices and sparkling water prices. 

```{r, message=FALSE, warning=FALSE, echo=FALSE, out.width='50%'}
# histogram and kernel density plot for margherita pizza prices (price_pizza variable)
ggplot( data = pizza_data , aes( x = price_pizza ) ) +
  geom_histogram( aes(y=..density..), fill = 'gold' , binwidth = 100 ) +
  geom_density( aes(y = ..density..) , fill = 'white' , bw = 100, alpha = 0.5 ) +
  labs(x='\n Price of Margherita Pizza (HUF)',y='Kernel Density (Percentage) \n',
       title= 'Distribution of Margherita Pizza Prices (binned every 100 HUF)')+
  scale_y_continuous(labels = scales::percent)+
  theme_light() +
  theme( panel.grid.minor.x = element_blank(), 
         plot.title = element_text(size = 12, face = "bold", hjust = 0.5 ) )

# histogram and kernel density plot for sparkling water prices (price_swater variable)
ggplot( data = pizza_data , aes( x = price_swater ) ) +
  geom_histogram( aes(y=..density..), fill = "dodgerblue3" , binwidth = 50 ) +
  geom_density( aes(y = ..density..) , fill = 'white' , bw = 50, alpha = 0.5 ) +
  labs(x='\n Price of 0.5L Sparkling Water (HUF)', y='Kernel Density (Percentage) \n') +
  ggtitle( 'Distribution of Sparkling Water Prices (binned every 50 HUF)' )+
  scale_y_continuous(labels = scales::percent)+
  theme_light() +
  theme( panel.grid.minor.x = element_blank(), 
         plot.title = element_text(size = 12, face = "bold", hjust = 0.5 ) )
```

### Visualizations of the price of margherita pizza conditioning on online vs offline price
```{r, message=FALSE, warning=FALSE, echo=FALSE, out.width='50%'}
# create factor variable for online vs offline price
pizza_data$online <- factor( pizza_data$delivery )

# histogram for margherita pizza prices conditioning on online vs offline prices
ggplot( data = pizza_data, aes( x = price_pizza, fill = online ) ) +
  geom_histogram( alpha = 0.7, binwidth = 60 ) +
  labs( x = '\n Price of Pizza', y = 'Frequency \n', fill = 'Online' ) +
  facet_wrap( ~online ) +
  annotate("rect",xmin=2500, xmax=3200, ymin=0, ymax=5, fill='gold', alpha=0.1) +
  theme_light() +
  theme( panel.grid.minor.x = element_blank(), 
         plot.title = element_text(size = 12, face = "bold", hjust = 0.5 ) ) +
  ggtitle( 'Conditional Histogram for the Price of Margherita Pizza' )

# boxplot for margherita pizza prices conditioning on online vs offline prices
ggplot( pizza_data, aes( x = online, y = price_pizza ) ) +
  geom_boxplot( color = "dodgerblue3", size = 0.7, width = 0.1, alpha = 1 ) +
  labs( x = '\n Online Price', y = 'Price of Pizza \n' ) +
  stat_boxplot( geom = "errorbar", width = 0.05,  size = 0.5 ) +
  stat_summary( fun = mean, geom = "point", shape = 20, size = 5, color = "deeppink4" ) +
  theme_light() +
  theme( plot.title = element_text(size = 12, face = "bold", hjust = 0.5 ) ) +
  ggtitle( 'Conditional Boxplot for the Price of Margherita Pizza' )
```

### Test of whether the online and offline prices of margherita pizza are the same
The hypotheses are about whether the offline versus online price difference is zero on average in population of products represented by the data. The null hypothesis is that online and offline prices of pizza margherita are the same in Budapest. The alternative hypothesis is that online and offline prices of pizza margherita are different in Budapest.
We fixed the level of significance at 5% then tested hypotheses.
```{r, '5' , echo=FALSE, fig.cap="Hypothesis Testing" , purl=FALSE}
test <- t.test(price_pizza ~ delivery, data = pizza_data)
print( paste0('P-value: ', round( test$p.value, 4 ) ) )
print( paste0('T-statistic: ', round( test$statistic, 4 ) ) )
print( paste0('Confidence Interval: ', round( test$conf.int, 1 ) ) )
```
Based on the results above since the p-value is larger than the level of significance we cannot reject the null hypothesis. The t-statistic is within +/- 2, also the CI is between -7 and and 542, so the difference between the online and offline prices can be zero. Thus, we can conclude that the offline and online prices of pizza margherita can be equal in Budapest.

### Summary of findings regarding unconditional and conditional price distributions
Based on the histograms of product prices it can be clearly seen that even though the price distribution for margherita pizza tends to have a few smaller modes, it closely resembles a normal distribution. With the help of binning, the distribution can be brought to look much closer like a normal distribution. The same cannot be said about the distribution of sparkling water prices, which showcases a heavy right skew, having a mean much higher than the median. This is perhaps caused by the large differences in sparkling water brands (from local Hungarian to expensive imported Italian water). As such, the range of products is much higher than with respect to the pizza. For further analysis, it would be worthwhile to inspect distributions of local sparkling water prices and imported water prices in separate graphs.

As for the conditional distribution of the price of margherita pizza it can be concluded that both the online and offline price distributions approximate a normal distribution. Furthermore, when comparing the two we can see that offline prices are higher on average than online prices since the mean of the former is higher than the latter. Also, on the histogram it is visible that the maximum online price is 2500 HUF while the maximum offline price is almost 3000 HUF. Lastly, the boxplot shows that the spread of offline prices is greater than that of the online prices.
