---
title: 'Budapest Pizza Project Report - KFC (Kata, Fanni, Cosmin) Team'
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r , include = FALSE, message=FALSE, warning=FALSE}

# loading up necessary packages
## tidyverse for tidyverse approach
## readxl for the table
## ggplot for visualizations
## moments for creating summary statistics table
library(tidyverse)
library(readxl)
library(ggplot2)
library(moments)

# loading in the data - change working directory in case of new user
data_in <- "C:/Users/acer/Desktop/OneDrive - Central European University/Courses/Fall_Term/Coding_1/data/Pizza"

# loading the pizza data table
pizza_data <- read_excel( paste0(data_in,"/raw/KFC-team_pizza_data.xlsx") )
```

### Data collection, difficulties & problems
The KFC team ([GitHub](https://github.com/cosmin-ticu/homework_codesANDmore_Coding1_MScBA/tree/master/Task1_KFC-team-coding)) chose to limit the data collection to the Budapest area, with inner city on-site locations metropolitan area delivery restaurants. The Google Maps API was used in order to compile the custom Google Maps shared lists of on-site locations, gather customer reviews and compute the travel time by foot between the restaurant and CEU (as a workaround to unpredictable car travel congestion). The choice of 0.5L sparkling water was convened with the drawback that the distribution of prices, brands and mark-up would be more heterogeneous than with the margherita pizza. The district, address and restaurant variables were added to have a unique identifier for every pizza place in case the dataset were to ever be expanded. The binary indicator variable 'delivery' differentiates between restaurants' menu and online merchants' prices. This ties into the 'delivery_site' column which designates the online vendor.

### Summary statistics

```{r, message=FALSE, warning=FALSE, echo=FALSE}
# summary statistics for the price_pizza variable
pizza_stat <- pizza_data %>% summarise(
  variable = 'price_pizza',
  n   = n(),
  Mean     = mean(price_pizza),
  Median   = median(price_pizza),
  Std      = sd(price_pizza),
  IQ_range = IQR(price_pizza), 
  Min      = min(price_pizza),
  Max      = max(price_pizza),
  Skew     = skewness(price_pizza))

# summary statistics for the price_swater variable
beverage_stat <- pizza_data %>% summarise(
  variable = 'price_swater',
  n   = n(),
  Mean     = round(mean(price_swater), 1),
  Median   = median(price_swater),
  Std      = round( sd(price_swater), 1),
  IQ_range = IQR(price_swater), 
  Min      = min(price_swater),
  Max      = max(price_swater),
  Skew     = round(skewness(price_swater)), 2)

# combine the two summary tables under one streamlined table
table_summary <- add_row(pizza_stat,beverage_stat)

# print said streamlined table
knitr::kable(table_summary,caption="Summary statistics for pizza margherita prices and for sparkling water prices in Budapest")
```

The average price of pizza margherita is 1958.25 HUF. As for the sparkling water, the average price is 518.5 HUF. The mean is higher than the median in case of the pizza and the water as well, indicating a somewhat skewed distribution with a longer right tail. In the next section, the distribution will be illustrated by histograms.

### Histograms of product prices (kernel density showcases skewness)

```{r, message=FALSE, warning=FALSE, echo=FALSE, out.width='50%'}
# histogram and kernel density plot overlay for margherita pizza prices (price_pizza variable)
ggplot( data = pizza_data , aes( x = price_pizza ) ) +
  geom_histogram( aes(y=..density..), fill = 'gold' , binwidth = 100 ) +
  geom_density( aes(y = ..density..) , fill = 'white' , bw = 100, alpha = 0.5 ) +
  labs(x='\n Price of Margherita Pizza (HUF)',y='Kernel Density (Percentage) \n',
       title= 'Distribution of Margherita Pizza Prices (binned every 100 HUF)')+
  scale_y_continuous(labels = scales::percent)+
  theme_light() +
  theme( panel.grid.minor.x = element_blank(), 
         plot.title = element_text(size = 12, face = "bold", hjust = 0.5 ) )

# histogram and kernel density plot overlay for sparkling water prices (price_swater variable)
ggplot( data = pizza_data , aes( x = price_swater ) ) +
  geom_histogram( aes(y=..density..), fill = "dodgerblue3" , binwidth = 50 ) +
  geom_density( aes(y = ..density..) , fill = 'white' , bw = 50, alpha = 0.5 ) +
  labs(x='\n Price of 0.5L Sparkling Water (HUF)', y='Kernel Density (Percentage) \n') +
  ggtitle( 'Distribution of Sparkling Water Prices (binned every 50 HUF)' )+
  scale_y_continuous(labels = scales::percent)+
  theme_light() +
  theme( panel.grid.minor.x = element_blank(), 
         plot.title = element_text(size = 12, face = "bold", hjust = 0.5 ) )
```

### Visualizations of the price of margherita pizza conditioning on online vs offline price

```{r, message=FALSE, warning=FALSE, echo=FALSE, out.width='50%'}
# create factor variable for online vs offline price
pizza_data$online <- factor( pizza_data$delivery )

# histogram for margherita pizza prices conditioning on online vs offline prices
ggplot( data = pizza_data, aes( x = price_pizza, fill = online ) ) +
  geom_histogram( alpha = 0.7, binwidth = 60 ) +
  labs( x = '\n Price of Pizza', y = 'Frequency \n', fill = 'Online' ) +
  facet_wrap( ~online ) +
  annotate("rect",xmin=2500, xmax=3200, ymin=0, ymax=5, fill='gold', alpha=0.1) +
  theme_light() +
  theme( panel.grid.minor.x = element_blank(), 
         plot.title = element_text(size = 12, face = "bold", hjust = 0.5 ) ) +
  ggtitle( 'Conditional Histogram for the Price of Margherita Pizza' )

# boxplot for margherita pizza prices conditioning on online vs offline prices
ggplot( pizza_data, aes( x = online, y = price_pizza ) ) +
  geom_boxplot( color = "dodgerblue3", size = 0.7, width = 0.1, alpha = 1 ) +
  labs( x = '\n Online Price', y = 'Price of Pizza \n' ) +
  stat_boxplot( geom = "errorbar", width = 0.05,  size = 0.5 ) +
  stat_summary( fun = mean, geom = "point", shape = 20, size = 5, color = "deeppink4" ) +
  theme_light() +
  theme( plot.title = element_text(size = 12, face = "bold", hjust = 0.5 ) ) +
  ggtitle( 'Conditional Boxplot for the Price of Margherita Pizza' )
```

### Test of whether the online and offline prices of margherita pizza are the same
The hypotheses are about whether the offline versus online price difference is zero on average in population of products represented by the data. The null hypothesis is that online and offline prices of pizza margherita are the same in Budapest. The alternative hypothesis is that online and offline prices of pizza margherita are different in Budapest.
We fixed the level of significance at 5% then tested hypotheses.
```{r, message=FALSE, warning=FALSE, echo=FALSE}

# save the t-test result into a corresponding tibble
test <- t.test(price_pizza ~ delivery, data = pizza_data)

# print out the statistics of interest
print( paste0('P-value: ', round( test$p.value, 4 ) ) )
print( paste0('T-statistic: ', round( test$statistic, 4 ) ) )
print( paste0('Confidence Interval: ', round( test$conf.int, 1 ) ) )
```
Based on the results above since the p-value is larger than the level of significance we cannot reject the null hypothesis. The t-statistic is within +/- 2, also the CI is between -7 and and 542, so the difference between the online and offline prices can be zero. Thus, we can conclude that the offline and online prices of pizza margherita can be equal in Budapest.

### Summary of findings regarding unconditional and conditional price distributions
Based on the histograms of product prices and the table of summary statistics it can be clearly seen that even though the price distribution for margherita pizza tends to have a few smaller modes, it closely resembles a normal distribution. With the help of binning, the distribution can be brought to look much closer like a normal distribution. The same cannot be said about the distribution of sparkling water prices, which showcases a heavy right skew, having a mean much higher than the median. This is perhaps caused by the large differences in sparkling water brands (from local Hungarian to expensive imported Italian water). As such, the range of products is much higher than with respect to the pizza. For further analysis, it would be worthwhile to inspect distributions of local sparkling water prices and imported water prices in separate graphs.

As for the conditional distribution of the price of margherita pizza it can be concluded that both the online and offline price distributions approximate a normal distribution. Furthermore, when comparing the two we can see that offline prices are higher on average than online prices since the mean of the former is higher than the latter. Also, on the histogram it is visible that the maximum online price is 2500 HUF while the maximum offline price is almost 3000 HUF. Lastly, the boxplot shows that the spread of offline prices is greater than that of the online prices.